---
title: "Homework 2 - tabs"
output:
  flexdashboard::flex_dashboard:
    navbar:
      - { icon: "fa-github", href: "https://github.com/Spatial-Data-Analytics-2025/Homework2", align: right }
---

```{r setup, include=FALSE}
library(flexdashboard)

```

## Sidebar {.sidebar}



link to Repo - https://github.com/Spatial-Data-Analytics-2025/Homework2.git

The three maps in this dashboard all focus on Chicago. If a gas station was within 75
meters of a school it was selected for relocation. 75 meters was chosen because it was the smallest distance where there was at least one example of a gas station being to close to two schools. When going in increments of 25 meters.

The first map provides a view of streets/locations where gas stations could be relocated to within Chicago.

The second map shows all instances where a gas station intercepts the 75m no gas station buffer zone that was coded around all schools in Chicago

The third map combines all relevant layers and illustrates the gas stations that need to be relocated along with possible relocation points.


## Column {.tabset .tabset-fade}


### Available Locations for Gas Stations

```{r}
readRDS("Routes_Map.rds")
```


### Intersection Map

```{r}
readRDS("Relocation_Map.rds")
```

### Map of Stations to Relocate

```{r}
readRDS("map_of_stations_to_relocate.rds")
```



