  ---
title: "Homework 2 - tabs"
output:
  flexdashboard::flex_dashboard:
    navbar:
      - { icon: "fa-github", href: "https://github.com/Spatial-Data-Analytics-2025/Homework2", align: right }
---

```{r setup, include=FALSE}
library(flexdashboard)

```

## Sidebar {.sidebar}

link to Repo - https://github.com/Spatial-Data-Analytics-2025/Homework2

The three maps in this dashboard all focus on Chicago. If a gas station was within 75
meters of a school it was selected for relocation. 75 meters was chosen because it was the smallest distance where there was at least one example of a gas station being too close to two schools (when measured in increments of 25 meters).

Map 1: Shows potential relocation routes for gas stations within Chicago.

Map 2: Shows intersections between gas stations and school buffer zones (75m).

Map 3: Combines all relevant layers to illustrate stations to relocate and potential relocation points.

## Column {.tabset .tabset-fade}


### Available Locations for Gas Stations

```{r}
readRDS("Routes_Map.rds")

```


### Intersection Map

```{r}
readRDS("Relocation_Map.rds")
```

### Map of Stations to Relocate

```{r}
readRDS("map_of_stations_to_relocate_final.rds")
```



